---
title: 'Velo Case'
author: 'Hasitha Josyula'
output:
  html_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

```


## Load packages and create empty data frame

```{r}
library(tidyverse)
v <- read_csv("velo.csv")

```


```{r}

v <- v %>% 
  mutate(checkout_system = factor(checkout_system, 
                                  levels = c("old", "new"))) # or

# v$checkout_system <- factor(v$checkout_system, levels = c("old", "new"))

```


t-test comparing the old and new systems:

```{r}
# T-test comparing old and new systems
t.test(filter(v, checkout_system == "new")$spent, 
       filter(v, checkout_system == "old")$spent)

# T-test comparing old and new systems for mobile users
t.test(filter(v, checkout_system == "new" & device == "mobile")$spent, 
       filter(v, checkout_system == "old" & device == "mobile")$spent)

```

### Q1

Fit a simple linear regression with `spent` as the target variable and `checkout_system` as the predictor. Based on the model summary, answer the following questions:

1. What is average spending for customers using 1) the new system and 2) the old system? This information can be extracted directly from the linear model output.

2. What is the difference in average customer spending between the new and old systems, and is the difference statistically significant at the p < .05 level?

3. Compare these results to those you obtained using a t-test in the last module (see the above output).

```{r}
model <- lm(spent ~ checkout_system, data = v)
model %>% summary
```


> 1. The average spending for customers using new checkout system is 2279.89(2217.15+62.74) and the average spending for customers using old checkout system is 2217.15 

> 2. The difference in average customer spending between the new and old systems is 62.74 for p-value 0.154 and the difference not statistically significant for this p-value.

> 3. The p-value for the new test is 0.154 and for old test the p-value is 0.1536 which are almost same for both linear model test and t-test.


### Q2

Fit a simple linear regression with `spent` as the target variable and `checkout_system` as the predictor, but include only customers who were using a mobile device. (Later you will learn how to fit this sort of regression using all the data, but for now subset the data to include only mobile users.) Answer these questions based on the model summary for this regression:

1. What is the difference in mobile customer spending between the new and old systems?

2. Is the difference statistically significant at the p < .05 level?

3. Compare these results to those you obtained using a t-test in the last module (see the above output).

Remember that the syntax for creating a simple linear regression model in R has the form:  `lm(y ~ x, data)`. This code will produce estimates of the model intercept and coefficients which you can use to assemble the regression equation:  y = intercept + coefficient * x.  To get more information about the model (including standard errors and p-values) use the generic `summary()` function. 


```{r}
model <- lm(spent ~ checkout_system, data = filter(v, device =='mobile'))
model %>% summary

```

> 1. The difference in mobile customer spending between the new and old systems is 148.08

> 2. The p-value is 0.01699 which less than the significant level 0.05. So the difference statistically significant.

> 3. When we compare the results from previous module, the p-value for t-test is 0.01655 which is almost same as the p-value for this linear model test which is 0.01699


###  Q3

Using the summary of the regression model object from Q2, calculate a 95% confidence interval (CI) for the `checkout_system` coefficient using 1.96 as the critical value. Interpret the CI: What does it mean exactly?

```{r}
#UpperCI:
((148.08) +(1.96 * 61.98))

#LowerCI:
((148.08) -(1.96 * 61.98))

```

> Using a critical value of 1.96, confidence intervals for the regression model with average differences of $148.08 resulted in confidence intervals of 269.5608 and 26.5992. This indicates that the data is stastically significant and rejecting the null hypothesis this shows that there is no increase in average spending.

### Q4

Based on the model output in Q2, along with the 95% CI you calculated in Q3, develop best and worst case revenue projections for the new checkout system.  What range of increased revenue might the company expect using the new checkout system (compared to the old system) and, based on this, does the coefficient estimate for `checkout_system`  have *practical* significance in your view? (Hint: multiply the lower and upper bounds of the CI you calculated in Q3 by an arbitrary number of customers.  That range, remember, is expressed in terms of average dollars per customer.)

A 95% CI for a coefficient represents the most likely range of values under repeated sampling.  Working with a range is advantageous.  Velo.com executives might well be interested in the low end of the range in order to assess the financial risks associated with implementing the new system.  Additionally, scaling up the average spending per customer gives you a way to convey the practical significance of using the new system. 

What do I mean by "scaling up"? For communication purposes it is often helpful to multiply averages, like the upper and lower bounds of the confidence interval, by some arbitrary scaling number (in this case, for example, 1000 or 5000 customers or whatever you think makes sense) so that a decision-maker can get a better sense of the overall impact to the business of a proposed change.  Think back to the Conley Fisheries case where you calculated that the maximum daily loss per boat was /$10,000.  By itself, that may seem like a sustainable loss. But remember there are 50 boats. So, really, to convey a complete sense of the risk the maximum per boat daily loss must be scaled up --- multiplied by --- the number of boats in the fleet. 

```{r}

#UpperCI:
((148.08) +(1.96 * 61.98)) * 3200

#LowerCI:
((148.08) -(1.96 * 61.98)) * 3200


```

> Considering an arbitrary value of 3200 new customers per month who are with the new systems, the upper and lower bounds of the CI are $862594.6 & $85117.44. From the analysis we can see the difference between the the lower and upper CI is large enough. So we can say that the data is pratically significant.



### Q5

What course of action should Sarah recommend to the management at velo.com based on this additional analysis? Please incorporate your analytic results from above in fashioning an answer. In particular, cite the results from the new analysis, the simple linear regression, and discuss your interpretation of the range you developed in Question 4.

> From the analysis done above, Sarah should make a recommendation to management to switch systems. We have seen that the average spending of old and new checkout systems are 2217.15 and 2279.89 respectively, also the is P- value is 0.15412 indicating the data is not stastically significant. But when we analysed only by considering mobile devices for new and old checkout systems,difference is 148.08 and we could see that the p-value is 0.01699 which is much lesser than 0.05. This indicates that the data is stastically significant. Also, when looking at confidence intervals with 95% and critical value 1.96, the upper and lower bounds are 862594.6 and 85117.44 and average difference is 148.08. To calculate the revenue projections, we considered a arbitary value of 3200 customers for new checkout system and found that the revenue is ranging between $85117.44 and $862594.6 which indicates that there is an increase in revenue of atleast $777477.16 when compared to old checkout system. So, from the above analysis, Sarah should definetely recommend Velo to change to new checkout system.
